### 2020-04-20 final_report/data.tex
add TODOs for the data section
rename sections to better reflect their content
redistribute more TODOs, rename sections (again)

\subsection{Data Description and Initial Sampling}
\label{sec:datadescription}

\newpage

@@

** Make sure discrete slices are mentioned before this **

@@

Question: is it accurate to say this represents nonlinear feature extraction? re my intro paragraph

\newpage

>>>>

\subsection{Feature Description}
\label{sec:feature-description}

TODO
\begin{enumerate}
	\item about single sphere OpenMC sim
	\item parameter listing
	\item continuous vs discrete features
	\item discrete embedding
\end{enumerate}

\subsection{Dataset Generation}
\label{sec:dataset-generation}

TODO
\begin{enumerate}
	\item grid search vs random sampling
	\item from a set of sampled points to evaluated TBR values
	\item tech deployed at Hypatia: dockerised sampler \& dataframe-driven querying
	\item run 0, 1, 2 parameters
\end{enumerate}

\subsection{Preprocessing}
\label{sec:preprocessing}

TODO
\begin{enumerate}
	\item discrete feature embedding
	\item standardisation
\end{enumerate}

@@

** TODO: Make sure discrete slices are mentioned before this **

@@

TODO: Question: is it accurate to say this represents nonlinear feature extraction? re my intro paragraph

TODO
\begin{enumerate}
	\item working principle
	\item application on single slice
	\item application on mixed slice data
\end{enumerate}
